---
title: "Package_Creation_01"
author: "Sylvain Dechaumet"
date: "9 mars 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PACKAGE CREATION IN RSTUDIO
- Install RStudio and GIT
- Create a GITHUB account
- In Rstudio/Tools/Global Option set git.exe adress
- Generate Secure Key and copy it on your github account
- In Rstudio/Tools/Project Option/Git, set your control system to git
- Install packages "devtools" and "roxygen2"
- Create Rstudio new project/package
- Write your function in ./R/xxxxx_file.R
- Use "document()" to compile your package

## To sync with github
- Create a new folder on github named as your package
- On your local package folder : right click and open git shell
- Follow instructions on site to link your local folder to github
- In Rstudio you can now push or pull your commit (version/revision)
- in the Git window (right). And you can check/load your package in the Build window.

## To sync with ssh key (no credentials needes to push)
- Create a ssh key with Rstudio
- Add it to your repository in github
- Change authentication method of git :
  - Git/Config/Shell, type : git config remote.origin.url git@github.com:Mystilivia/SDjoygret.git
  - Try to push something, soft will ask you to confirm the use of ssh key : answer "yes"
  - Done

## To install the package
- devtools::install_github("Mystilivia/SDjoygret")

```{r Compile documentation, warning=FALSE, include=FALSE}
library(devtools)
document()
```





